---
title: "Partial Plots for 3 way FWI Split"
author: "Anna Talucci"
date: "11/10/2021"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview
Script adapted from Areil Muldoon and Garrett Meigs

September 2019: Extra fun with partial plots.  This script is designed to use brt model runs saved as .Rdas.

Data from BRTAnalysis-SubsetData

# Goal: Overlay partial-dependence plots from multiple models.

NOte: the y-axis of the BRT model are referred to as the fitted function, for a binomial distribtuion this fitted function is the loggit scale. To convert back to a probability we can use the plogis() function. We will leave the y-axix on the logit scale but also add a line for a high probability

setwd("K:/Papers/Meigs_Refugia2_LateSuccessionalForests/r_files_brt")   ### Change to wherever you put the code files sourced below

# Load packages
```{r message=FALSE, warning=FALSE}
library(gbm)
library(dismo)
library(purrr) # for looping
library(ggplot2)
library(scales)
library(dplyr) # for data manip
library(cowplot)
```

# BRT Models

Model         | Name        | FWI        | Variables
------------- | ----------- | ---------- | -------------------------------------------
brt.model1    | Full        | Full Range | Prefire, outbreak, weather, topography
brt.model2    | Hi          | Hi  only   | Prefire, outbreak, weather, topography

brt.model3    | moderate          | moderate only    | Prefire, outbreak, weather, topography
brt.model4   | benign      |





# Load BRT Models 
Load BRT models that are saved during the model as .Rda files in the working directory. Models are assembled and run in the script 'BRTAnalyses'
```{r}
load(file = "../outputs/BRTmodelsFWI3_v2/BRT1_model.rda")
brt.model1 = brt.model1

load(file = "../outputs/BRTmodelsFWI3_v2/BRT2_model.rda")
brt.model2 = brt.model2

load(file = "../outputs/BRTmodelsFWI3_v2/BRT3_model.rda")
brt.model3 = brt.model3

load(file = "../outputs/BRTmodelsFWI3_v2/BRT4_model.rda")
brt.model4 = brt.model4
```

# Data

```{r}
data = read.csv("../data/CombinedData/CombineData.csv") 
```

```{r}
head(data)
```

# Manuscript figure

## models 
Make list of models and variables
mods4 = list(Hi_4var = brt.model1, Mod_4var = brt.model2, Full_4var = brt.model6)
vars4 = c("dndmi", "elevation", "fwi", "ndviprefire")
names(vars4) = vars4
vars4
```{r}
mods4 = list(Full= brt.model1, Extreme = brt.model2, Moderate = brt.model3, Benign = brt.model4)
vars4 = c("dndmi", "elevation", "fwi", "ndviprefire")
names(vars4) = vars4
vars4
```

Nicer variable names for x axis labels Must be in same order as vars
```{r}
x_names4 = c("Outbreak severity (dNDMI)", "Elevation (m)", "Fire Weather (FWI)", "Prefire vegetation (NDVI)")
```

### Predicted dataset 
Use nested loops for each variable and then each model within each variable

 For outer loop use map() or lapply()
 For the inner loop use imap_dfr() to use models and model names and bind together

 Work out approach with a single variable
 Goal is to get a dataset with predictions from all models stacked together for one x variable

### Loop through single varible
```{r}
pred_test4 = map(vars4[[1]], function(variable) {
     imap_dfr(mods4, function(Model, mod.name) {
          preddat = plot.gbm(Model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$Model = mod.name
          preddat
     })
})

pred_test4
```

### Loop through all Varaibles 
If that worked, loop through all variables
```{r}
pred_mods4 = map(vars4, function(variable) {
     imap_dfr(mods4, function(model, mod.name) {
          preddat = plot.gbm(model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$model = mod.name
          preddat
     })
})
```

Figure out plot limits (if want all the same) by binding all groups together and calculating min and max center_y
```{r}
range(bind_rows(pred_mods4)$center_y)
```
### Plot
```{r}
ggplot(data = pred_mods4[[1]], aes(x = x, y = center_y, linetype = model, color = model) ) +
        geom_smooth(span = 0.5, se = TRUE) + # choose span? 
        scale_color_manual(values = c('#d7191c','#fdae61','#abd9e9','#2c7bb6'), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        scale_linetype_manual(values = c("solid", "longdash", "twodash", "dotdash"), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        labs(x = x_names4[[1]]) +
        theme_bw(base_size = 12) +
        theme(axis.text.x = element_text(size = 10, color = "black"),
              axis.text.y = element_text(size = 10, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "bottom",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)

```
### Plot with improved x axis names ----
```{r}
model_id <- ggplot(data = pred_mods4[[1]], aes(x = x, y = center_y, linetype = model, color = model) ) +
        geom_smooth(span = 0.5, se = TRUE) + # choose span? 
        scale_color_manual(values = c('#d7191c','#fdae61','#abd9e9','#2c7bb6'), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        scale_linetype_manual(values = c("solid", "longdash", "twodash", "dotdash"), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        labs(x = x_names4[[1]]) +
        theme_bw(base_size = 12) +
        theme(axis.text.x = element_text(size = 10, color = "black"),
              axis.text.y = element_text(size = 10, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "bottom",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)+
        scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")

model_id
```
Leaving legend to indicate multiple models plotted.
# Colors

cbbBTCodesPalette <- c("#009E73", "#0072B2", "#000000", "#E69F00", "#56B4E9", "#F0E442", "#CC79A7", "#D55E00")

Original colors
'#d7191c','#fdae61','#abd9e9','#2c7bb6'
scale_linetype_manual(values = c("solid", "longdash", "twodash", "dotdash"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate", "Benign"), guide = guide_legend(reverse=FALSE)) +
### Figure Legend
```{r}
BC_leg = ggplot(data = pred_mods4[[1]], aes(x = x, y = center_y, color = model) ) +
        geom_smooth(span = 0.5, se = TRUE, aes(color = model), alpha = 0.5) + # choose span? 
        scale_color_manual(values = c("#999999", "#D55E00", "#F0E442", "#56B4E9"), name = "Burning conditions", breaks = c("Full", "Extreme", "Moderate", "Benign"), labels=c("Full", "Extreme", "Moderate", "Benign"), guide = guide_legend(reverse=FALSE)) +
        
        labs(y = "Fitted Function",
             x = x_names4[[1]]) +
        theme_bw(base_size = 12) +
        theme(axis.text.x = element_text(size = 10, color = "black"),
              axis.text.y = element_text(size = 10, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "right",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)+
        scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")

BC_leg
```

### Figure Legend
 labels=c("Full", "Extreme", "Moderate", "Benign")
```{r}
legBottom = ggplot(data = pred_mods4[[1]], aes(x = x, y = center_y, color = model) ) +
        geom_smooth(span = 0.5, se = TRUE) + # choose span? 
         scale_color_manual(values = c("#999999", "#D55E00", "#F0E442", "#56B4E9"), name = "Burning conditions", breaks = c("Full", "Extreme", "Moderate", "Benign"), labels=c("Full", "Extreme", "Moderate", "Benign"), guide = guide_legend(reverse=FALSE)) +
        
        labs(y = "Fitted Function",
             x = x_names4[[1]]) +
        theme_bw(base_size = 12) +
        theme(axis.text.x = element_text(size = 10, color = "black"),
              axis.text.y = element_text(size = 10, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "bottom",
              legend.title = element_text(size = 10),
              legend.text = element_text(size = 10)) +
  theme(legend.key.height = unit(.2, 'in'), 
        legend.key.width = unit(.3, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)))  + 
  guides(fill = guide_legend(ncol=1), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
  guides(color=guide_legend(override.aes=list(fill=NA))) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0) +
        geom_rug(sides="b") +
        scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")

legBottom
```
### Plotting function ----
Note: plot.margin - t,r,b,l

Adjust plot margins for compiling a panel figure with cowplot.
['#8c510a','#d8b365','#f6e8c3','#c7eae5','#5ab4ac','#01665e']
```{r}
pardep_plot_mods4 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, color = model) ) +
    geom_smooth(span = 0.5, se = TRUE, level = 0.90, fullrange = FALSE, aes(fill = model),size = .5, alpha = 0.25) + # choose span? 
    scale_color_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
    scale_fill_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
                labs(x = x_var) +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")
}

pardep_plot_mods4(data = pred_mods4[[1]], x_var = x_names4[[1]])
```

```{r eval=FALSE, include=FALSE}
pardep_plot_mods4 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, color = model) ) +
    geom_smooth(span = 0.5, se = TRUE, level = 0.90, fullrange = FALSE, aes(fill = model)) + # choose span? 
    scale_color_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
                labs(x = x_var) +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")
}

pardep_plot_mods4(data = pred_mods4[[1]], x_var = x_names4[[1]])
```

### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
all_mod_plots4 = map2(pred_mods4, x_names4, pardep_plot_mods4)
all_mod_plots4
```


# Function to go from logit to probability
```{r}
logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
```

```{r}
logit2prob(-2.197225)
logit2prob(-0.8472979)

logit2prob(0)

logit2prob(0.8472979)
logit2prob(2.197225)
```

## Manuscript Figure


```{r}
legend_bottom <- get_legend(legBottom) 
```
Order plots
-- FWI
-- Elevation
-- NDVI
-- dNDMI


```{r fig.height=5, fig.width=6}
msplot1 = cowplot::plot_grid( all_mod_plots4$fwi, all_mod_plots4$ndviprefire,  all_mod_plots4$elevation, all_mod_plots4$dndmi, ncol = 2) +
  
    draw_label("benign", x = .16, y = .62, size = 9) +
    draw_label("moderate", x = .27, y = .62, size = 9) +
   draw_label("extreme", x = .42, y = .62, size = 9) +
    draw_label("dead/\nsparse", x = .75, y = .63, size = 9) +
    draw_label("live/\ndense", x = .9, y = .63, size = 9) +
      draw_label("low", x = .2, y = .12, size = 9) +
   draw_label("high", x = .4, y = .12, size = 9) +
   draw_label("no\nmortality", x = .7, y = .14, size = 9) +
   draw_label("high\nmortality", x = .9, y = .14, size = 9) +
   draw_label("(a)", x = .14, y = .97, size = 10) +
   draw_label("(b)", x = .64, y = .97, size = 10) +
   draw_label("(c)", x = .14, y = .47, size = 10) +
   draw_label("(d)", x = .64, y = .47, size = 10) 

msplot1
```

```{r fig.height=5.25, fig.width=6}
grid_msplot = cowplot::plot_grid(msplot1, legend_bottom, ncol=1, rel_heights = c(1, .1))

grid_msplot
```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/PartialPlot3FWI_v2.tiff", plot = grid_msplot, width = 6, height =5.25, units = c("in"), dpi=600, bg = "white" )
```

# With Rug plot
```{r}
head(data)
```
### Plotting function ----
Note: plot.margin - t,r,b,l

Adjust plot margins for compiling a panel figure with cowplot.
['#8c510a','#d8b365','#f6e8c3','#c7eae5','#5ab4ac','#01665e']
```{r}
pardep_plot_mods4 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, color = model) ) +
    geom_smooth(span = 0.5, se = TRUE, level = 0.90, fullrange = FALSE, aes(fill = model),size = .5, alpha = 0.25) + # choose span? 
    scale_color_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
    scale_fill_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
                labs(x = x_var) +
    geom_rug(sides="b") +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")
}

pardep_plot_mods4(data = pred_mods4[[1]], x_var = x_names4[[1]])
```

### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
all_mod_plots4 = map2(pred_mods4, x_names4, pardep_plot_mods4)
all_mod_plots4
```



### Manuscript Figure


```{r}
legend_bottom <- get_legend(legBottom) 
```
Order plots
-- FWI
-- Elevation
-- NDVI
-- dNDMI


```{r fig.height=5, fig.width=6}
msplot2 = cowplot::plot_grid( all_mod_plots4$fwi, all_mod_plots4$ndviprefire,  all_mod_plots4$elevation, all_mod_plots4$dndmi, ncol = 2) +
  
    draw_label("benign", x = .16, y = .62, size = 9) +
    draw_label("moderate", x = .27, y = .62, size = 9) +
   draw_label("extreme", x = .42, y = .62, size = 9) +
    draw_label("dead/\nsparse", x = .75, y = .63, size = 9) +
    draw_label("live/\ndense", x = .9, y = .63, size = 9) +
      draw_label("low", x = .2, y = .12, size = 9) +
   draw_label("high", x = .4, y = .12, size = 9) +
   draw_label("no\nmortality", x = .7, y = .14, size = 9) +
   draw_label("high\nmortality", x = .9, y = .14, size = 9) +
   draw_label("(a)", x = .14, y = .97, size = 10) +
   draw_label("(b)", x = .64, y = .97, size = 10) +
   draw_label("(c)", x = .14, y = .47, size = 10) +
   draw_label("(d)", x = .64, y = .47, size = 10) 

msplot2
```

```{r fig.height=5.25, fig.width=6}
grid_msplot2 = cowplot::plot_grid(msplot2, legend_bottom, ncol=1, rel_heights = c(1, .1))

grid_msplot2
```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/PartialPlot3FWI_v2_rug.tiff", plot = grid_msplot2, width = 6, height =5.25, units = c("in"), dpi=600, bg = "white" )
```

# Stagered rug plots
```{r}
rug_stag_pardep_plot_mods4 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, color = model) ) +
    geom_smooth(span = 0.5, se = TRUE, level = 0.90, fullrange = FALSE, aes(fill = model),size = .5, alpha = 0.25) + # choose span? 
    scale_color_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
    scale_fill_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
                labs(x = x_var) +
    geom_rug(data = subset(data, model=="Extreme"),sides="t") +
    geom_rug(data = subset(data, model=="Moderate"),sides="b", outside=F) +
    geom_rug(data = subset(data, model=="Benign"),sides="t", outside=T) +
    coord_cartesian(clip="off") +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(1, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")
}

rug_stag_pardep_plot_mods4(data = pred_mods4[[1]], x_var = x_names4[[1]])
```

### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
all_mod_plots4_stag = map2(pred_mods4, x_names4, rug_stag_pardep_plot_mods4)
all_mod_plots4_stag
```



### Manuscript Figure


```{r}
legend_bottom <- get_legend(legBottom) 
```
Order plots
-- FWI
-- Elevation
-- NDVI
-- dNDMI


```{r fig.height=5, fig.width=6}
msplot3 = cowplot::plot_grid( all_mod_plots4_stag$fwi, all_mod_plots4_stag$ndviprefire,  all_mod_plots4_stag$elevation, all_mod_plots4_stag$dndmi, ncol = 2) +
  
    draw_label("benign", x = .16, y = .62, size = 9) +
    draw_label("moderate", x = .27, y = .62, size = 9) +
   draw_label("extreme", x = .42, y = .62, size = 9) +
    draw_label("dead/\nsparse", x = .75, y = .63, size = 9) +
    draw_label("live/\ndense", x = .9, y = .63, size = 9) +
      draw_label("low", x = .2, y = .12, size = 9) +
   draw_label("high", x = .4, y = .12, size = 9) +
   draw_label("no\nmortality", x = .7, y = .14, size = 9) +
   draw_label("high\nmortality", x = .9, y = .14, size = 9) +
   draw_label("(a)", x = .14, y = .95, size = 10) +
   draw_label("(b)", x = .64, y = .95, size = 10) +
   draw_label("(c)", x = .14, y = .45, size = 10) +
   draw_label("(d)", x = .64, y = .45, size = 10) 

msplot3
```

```{r fig.height=5.25, fig.width=6}
grid_msplot4 = cowplot::plot_grid(msplot3, legend_bottom, ncol=1, rel_heights = c(1, .1))

grid_msplot4
```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/PartialPlot3FWI_v2_rugstaggered.tiff", plot = grid_msplot4, width = 6, height =5.25, units = c("in"), dpi=600, bg = "white" )
```


# Fitted Function with Stagered rug plots
```{r}
fitted_pardep_plot_mods4 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, color = model) ) +
    geom_smooth(span = 0.5, se = TRUE, level = 0.90, fullrange = FALSE, aes(fill = model),size = .5, alpha = 0.25) + # choose span? 
    scale_color_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
    scale_fill_manual(values = c("#56B4E9", "#D55E00", "#999999", "#F0E442")) +
                labs(x = x_var) +
    geom_rug(data = subset(data, model=="Extreme"),sides="t") +
    geom_rug(data = subset(data, model=="Moderate"),sides="b", outside=F) +
    geom_rug(data = subset(data, model=="Benign"),sides="t", outside=T) +
    coord_cartesian(clip="off") +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(1, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                scale_x_continuous(labels = comma) +
                ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                
                scale_y_continuous( name="Fitted function")
}

fitted_pardep_plot_mods4(data = pred_mods4[[1]], x_var = x_names4[[1]])
```

### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
all_mod_plots4_fitted = map2(pred_mods4, x_names4, fitted_pardep_plot_mods4)
all_mod_plots4_fitted
```



### Manuscript Figure


```{r}
legend_bottom <- get_legend(legBottom) 
```
Order plots
-- FWI
-- Elevation
-- NDVI
-- dNDMI


```{r fig.height=5, fig.width=6}
msplot5 = cowplot::plot_grid( all_mod_plots4_fitted$fwi, all_mod_plots4_fitted$ndviprefire,  all_mod_plots4_fitted$elevation, all_mod_plots4_fitted$dndmi, ncol = 2) +
  
    draw_label("benign", x = .15, y = .615, size = 9) +
    draw_label("moderate", x = .27, y = .615, size = 9) +
   draw_label("extreme", x = .425, y = .615, size = 9) +
    draw_label("dead/\nsparse", x = .75, y = .63, size = 9) +
    draw_label("live/\ndense", x = .9, y = .63, size = 9) +
      draw_label("low", x = .17, y = .12, size = 9) +
   draw_label("high", x = .4, y = .12, size = 9) +
   draw_label("no\nmortality", x = .7, y = .32, size = 9) +
   draw_label("high\nmortality", x = .9, y = .14, size = 9) +
   draw_label("(a)", x = .14, y = .95, size = 10) +
   draw_label("(b)", x = .64, y = .95, size = 10) +
   draw_label("(c)", x = .14, y = .45, size = 10) +
   draw_label("(d)", x = .64, y = .45, size = 10) 

msplot5
```

```{r fig.height=5.25, fig.width=6}
grid_msplot6 = cowplot::plot_grid(msplot5, legend_bottom, ncol=1, rel_heights = c(1, .1))

grid_msplot6
```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/PartialPlot3FWI_v2_Rug_fitted.tiff", plot = grid_msplot6, width = 6, height =5.25, units = c("in"), dpi=600, bg = "white" )
```

**THE END**