---
title: "BRT Analysis"
author: "Anna Talucci"
date: "05/24/2021"
outputs: html_document
---

# Overview

## Notes

Copied from repo beetle-fire-landscape-bc BRTAnalyses.RMD


--Beetle vs. Fuels

Boosted Regression Trees in R 
Note: this is a cut-down version of a tutorial prepared by Jane Elith and John Leathwick
Adapted by Chris Dunn for fire risk assessment
Adapted by Garrett Meigs for analysis of fire refugia
Complementary to Krawchuk et al. 2016 Ecosphere scripts



# Clear workspace

```{r}
rm(list=ls()) 
```


## Set libraries
```{r include=FALSE}

library(devtools)
library(gbm)
library(foreign)
library(dismo)
library(dplyr)
library(splines)
library(ggplot2)
```

##Install additional BRT functions 
These are provided in a file such as ?brt.functions.R? and can be loaded into R using the source command, e.g.:
```{r}
source("../function/brt.functions.R")
```

# Import data
```{r}
model.data = read.csv("../data/GRTS_Samples/2019-09-02_AllSamples.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

# Check dimensions, column names and order for later operations, and summary statistics
```{r}
head(model.data)
```

## Subset by FWI
presence/absence (1/0) of high burn severity 
```{r}
model.data$fwi_lohi = ifelse(model.data$fwi <= 29, 1, 2)
model.data$reclass_rdnbr_mt = ifelse(model.data$rdnbr < 316, 0, 1)
model.data$reclass_rdnbr_fs = ifelse(model.data$rdnbr < 600, 0, 1)
 
```
2 is anything greater then 29 and 1 is anything less than or equal to 29
```{r}
head(model.data)
```

```{r}
dim(model.data)
```

```{r}
model.data.lo = subset(model.data, fwi_lohi == "1")
```

```{r}
dim(model.data.lo)
```
```{r}
model.data.lo %>%
  count(reclass_rdnbr_fs) %>%
  group_by(reclass_rdnbr_fs) 
```

```{r}
model.data.lo %>%
  count(reclass_rdnbr_mt) %>%
  group_by(reclass_rdnbr_mt) 
```

```{r}
model.data.hi = subset(model.data, fwi_lohi == "2")
```

```{r}
dim(model.data.hi)
```

```{r}
model.data.hi %>%
  count(reclass_rdnbr_mt) %>%
  group_by(reclass_rdnbr_mt) 
```

```{r}
model.data.hi %>%
  count(reclass_rdnbr_fs) %>%
  group_by(reclass_rdnbr_fs) 
```


```{r}
head(model.data)
```

```{r}
names(model.data)
```


# MODEL 1 


## Model 1: Split FWI - FWI HI 
Run the BRT model
with explanatory variables: 
*  dndmi (15)
*  elevation(17)
*  fwi (18)
*  ndviprefire (21)
*  rdnbr_class(26)
*  reclass_rdnbr_mt (34)
*  reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.model1 <- gbm.step(data=model.data.hi,
    gbm.x = c(15,17,18,21), ## 11 variables
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model outputs
```{r}
summary(brt.model1,
        cBars=length(brt.model1$var.names),
        n.trees=brt.model1$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model outputs as external object for mapping later or posterity

```{r}
save(brt.model1, file = "../outputs/brtmodels/BRT_model1.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../outputs//brtmodels/BRT_model1.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.model1, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r eval=FALSE, include=FALSE}
gbm.plot(brt.model1, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-02_BRT_model1_plots.pdf")
dev.off()
```
```{r eval=FALSE, include=FALSE}
gbm.plot.fits(brt.model1)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-02_BRT_model1_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.model1)
find.int$rank.list
find.int$interactions
```

## Calculate outputs stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputss from the BRT code.

tot.n=nrow(temp2)
    y.perc=round(nrow(temp2[temp2$yvar==1,])/tot.n,2)
```{r}
tot.n=nrow(model.data.hi)
y.perc=round(nrow(model.data.hi[model.data.hi$yvar==1,])/tot.n,2)
vnames=row.names(brt.model1$contributions)
rel.inf=round(brt.model1$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.model1$self.statistics$mean.resid/brt.model1$self.statistics$mean.null),2)
roc.mean=round(mean(brt.model1$cv.roc.matrix),2)
cv.dev.mean=round(brt.model1$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.model1$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.model1$cv.statistics$discrimination.mean,2)
```

```{r}
tot.n
model.data.hi$reclass_rdnbr_fs==1
y.perc
```

```{r}
BRT.model1.sum=data.frame(tot.n, y.perc, brt.model1$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.model1.sum, '../outputs/brtSummary/BRT_model1_sum.csv', row.names = F)
BRT.model1.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.model1.relinf, '../outputs/brtSummary/BRT_model1_relinf.csv', row.names = F)
```