---
title: "Interaction Effects"
author: "Anna Talucci"
date: '2022-09-02'
output: html_document
---



# Load BRT Models 
Load BRT models that are saved during the model as .Rda files in the working directory. Models are assembled and run in the script 'BRTAnalyses'
```{r}
load(file = "../outputs/BRTmodelsFWI3_v2/BRT1_model.rda")
brt.model1 = brt.model1

load(file = "../outputs/BRTmodelsFWI3_v2/BRT2_model.rda")
brt.model2 = brt.model2

load(file = "../outputs/BRTmodelsFWI3_v2/BRT3_model.rda")
brt.model3 = brt.model3

load(file = "../outputs/BRTmodelsFWI3_v2/BRT4_model.rda")
brt.model4 = brt.model4
```

# Plot Themes
```{r}
bar_theme = theme_bw() + 
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
          axis.title.x = element_text(size = 9),
        axis.text.x = element_text(size = 6, color = "black"),
        axis.text.y = element_text(size = 6, color = "black"),
        axis.line = element_line(colour = "black")) 
```

# Data
# Data
## Interaction table
```{r}
ie_data = read.csv("../data/Interactions/FWI3Split_v2_Interactions.csv", header=TRUE, sep = ",", strip.white = TRUE)
```
## Model
```{r}
model.data = read.csv("../data/CombinedData/CombineDataCat3FWI.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
head(model.data)
```

## Select Columns 
Select variable columns
*  dndmi 
*  elevation
*  fwi 
*  ndviprefire

Mutate to add columns for classifying FWI and RdNBR
FWI lo=1, hi=2 
2 is anything greater then 29 and 1 is anything less than or equal to 29
Rdnbr low = 0, high=1


```{r}
data_full = model.data %>%
  dplyr::select(dndmi, elevation, fwi, ndviprefire, rdnbr_class)
data_full
```

```{r}

data_ben = model.data %>%
  filter(fwi_cat == "benign") %>%
  dplyr::select(dndmi, elevation, fwi, ndviprefire, rdnbr_class)
data_ben
```

```{r}

data_mod = model.data %>%
  filter(fwi_cat == "moderate") %>%
  dplyr::select(dndmi, elevation, fwi, ndviprefire, rdnbr_class)
data_mod
```


```{r}

data_ext= model.data %>%
  filter(fwi_cat == "extreme") %>%
  dplyr::select(dndmi, elevation, fwi, ndviprefire, rdnbr_class)
data_ext
```



# Model 1


```{r}
find.int = gbm.interactions(brt.model1)
find.int$rank.list
find.int$interactions
```

## Pair Wise

```{r}
interact.gbm(brt.model1, data_full, i.var=c("dndmi", "elevation"), n.trees = brt.model1$n.trees)
```
```{r}
interact.gbm(brt.model1, data_full, i.var=c("fwi", "ndviprefire"), n.trees = brt.model1$n.trees)
```
```{r}
interact.gbm(brt.model1, data_full, i.var=c("elevation", "ndviprefire"), n.trees = brt.model1$n.trees)
```
```{r}
interact.gbm(brt.model1, data_full, i.var=c("elevation", "fwi"), n.trees = brt.model1$n.trees)
```
```{r}
interact.gbm(brt.model1, data_full, i.var=c("dndmi", "fwi"), n.trees = brt.model1$n.trees)
```
```{r}
interact.gbm(brt.model1, data_full, i.var=c("dndmi", "ndviprefire"), n.trees = brt.model1$n.trees)
```
### All variable
```{r}
interact.gbm(brt.model1, data_mod, i.var=c("dndmi", "ndviprefire", "fwi", "elevation"), n.trees = brt.model1$n.trees)
```


# Model 2 Extreme
```{r}
find.int = gbm.interactions(brt.model2)
find.int$rank.list
find.int$interactions
```

### Pairwise
```{r}
interact.gbm(brt.model2, data_ext, i.var=c("dndmi", "elevation"), n.trees = brt.model2$n.trees)
```
```{r}
interact.gbm(brt.model2, data_ext, i.var=c("fwi", "ndviprefire"), n.trees = brt.model2$n.trees)
```
```{r}
interact.gbm(brt.model2, data_ext, i.var=c("elevation", "ndviprefire"), n.trees = brt.model2$n.trees)
```
```{r}
interact.gbm(brt.model2, data_ext, i.var=c("elevation", "fwi"), n.trees = brt.model2$n.trees)
```
```{r}
interact.gbm(brt.model2, data_ext, i.var=c("dndmi", "fwi"), n.trees = brt.model2$n.trees)
```
```{r}
interact.gbm(brt.model2, data_ext, i.var=c("dndmi", "ndviprefire"), n.trees = brt.model2$n.trees)
```
### All variable
```{r}
interact.gbm(brt.model2, data_ext, i.var=c("dndmi", "ndviprefire", "fwi", "elevation"), n.trees = brt.model2$n.trees)
```

# Model 3 Moderate
```{r}
find.int = gbm.interactions(brt.model3)
find.int$rank.list
find.int$interactions
```
### Pairwise
```{r}

interact.gbm(brt.model3, data_mod, i.var=c("dndmi", "elevation"), n.trees = brt.model3$n.trees)
```

```{r}

interact.gbm(brt.model3, data_mod, i.var=c("fwi", "ndviprefire"), n.trees = brt.model3$n.trees)
```
```{r}

interact.gbm(brt.model3, data_mod, i.var=c("elevation", "ndviprefire"), n.trees = brt.model3$n.trees)
```

```{r}

interact.gbm(brt.model3, data_mod, i.var=c("elevation", "fwi"), n.trees = brt.model3$n.trees)
```

```{r}

interact.gbm(brt.model3, data_mod, i.var=c("dndmi", "fwi"), n.trees = brt.model3$n.trees)
```

```{r}

interact.gbm(brt.model3, data_mod, i.var=c("dndmi", "ndviprefire"), n.trees = brt.model3$n.trees)
```

### All variable
```{r}

interact.gbm(brt.model3, data_mod, i.var=c("dndmi", "ndviprefire", "fwi", "elevation"), n.trees = brt.model3$n.trees)
```

# Model 4 
```{r}
find.int = gbm.interactions(brt.model4)
find.int
find.int$rank.list
find.int$interactions
```
### Pairwise
```{r}

interact.gbm(brt.model4, data_ben, i.var=c("dndmi", "elevation"), n.trees = brt.model4$n.trees)
```

```{r}

interact.gbm(brt.model4, data_ben, i.var=c("fwi", "ndviprefire"), n.trees = brt.model4$n.trees)
```
```{r}

interact.gbm(brt.model4, data_ben, i.var=c("elevation", "ndviprefire"), n.trees = brt.model4$n.trees)
```

```{r}

interact.gbm(brt.model4, data_ben, i.var=c("elevation", "fwi"), n.trees = brt.model4$n.trees)
```

```{r}

interact.gbm(brt.model4, data_ben, i.var=c("dndmi", "fwi"), n.trees = brt.model4$n.trees)
```

```{r}

interact.gbm(brt.model4, data_ben, i.var=c("dndmi", "ndviprefire"), n.trees = brt.model4$n.trees)
```

### All varaibles
```{r}

interact.gbm(brt.model4, data_ben, i.var=c("dndmi", "ndviprefire", "fwi", "elevation"), n.trees = brt.model4$n.trees)
```


# Figure
```{r}
ie_data
```
```{r}
as.factor(ie_data$weather)
ie_data2 = ie_data %>% 
  mutate(weather = factor(weather, levels=c("Benign", "Moderate", "Extreme", "Full"))) %>% drop_na(.)
```

```{r}
ie_data3 <- na.omit(ie_data2)
ie_data3
```
```{r}
ggplot(ie_data2, aes(x = interaction, y = hstat,  fill = weather)) +
  geom_segment(aes(x = interaction, xend = interaction, y = 0, yend = hstat),
               color = "gray", lwd = 1) +
  geom_point(size = 7.5, pch = 21, bg = 4, col = 1, ) +
  geom_text(aes(label = hstat), color = "white", size = 3) +
  scale_fill_manual(values = c("#999999", "#D55E00", "#F0E442", "#56B4E9"), name = "Model", breaks = c("Full", "Extreme", "Moderate", "Benign"), labels=c("Full", "Extreme", "Moderate", "Benign"), guide = guide_legend(reverse=FALSE))  +
  coord_flip() +
  theme_minimal()
```

```{r}
shading <- data.frame(min = seq(from = 0.5, to = max(as.numeric(as.factor(ie_data2$interaction))), by = 1), max = seq(from = 1.5, to = max(as.numeric(as.factor(ie_data2$interaction))) + 0.5, by = 1), col = c(0,1))
```
## Plot
```{r fig.height=4, fig.width=3}
plot1 = ggplot(ie_data3) +
    geom_linerange(aes(x = interaction, ymin = 0, ymax = hstat, colour = weather), 
                   position = position_dodge(width = 1), show.legend = FALSE)+
    geom_point(aes(x = interaction, y = hstat, colour = weather),
               position = position_dodge(width = 1), size = 4) +
  
  geom_rect(data = shading, aes(xmin = min, xmax = max, ymin = -Inf, ymax = Inf, fill = factor(col), alpha = 0.1), show.legend = FALSE) +
  scale_fill_manual(values = c("white", "gray90")) +
  geom_linerange(aes(x = interaction, ymin = 0, ymax = hstat, colour = weather), 
                   position = position_dodge(width = 1), show.legend = FALSE)+
    geom_point(aes(x = interaction, y = hstat, colour = weather),
               position = position_dodge(width = 1), size = 4) +
  scale_colour_manual(values = c("#999999", "#D55E00", "#F0E442", "#56B4E9"), name = "Model", breaks = c("Full", "Extreme", "Moderate", "Benign"), labels=c("Full", "Extreme", "Moderate", "Benign"), guide = guide_legend(reverse=FALSE))  +
    coord_flip() +
    bar_theme +
  ylab('Two-way interaction strength') +
  scale_x_discrete(
    "Explanatory Variables",
    labels = c(
      "FWI:NDVI Prefire" = "FWI:\nNDVI Prefire",
      "FWI:Elevation" = "FWI:\nElevation",
      "Elevation:NDVI Prefire" = "Elevation:\nNDVI Prefire",
      "FWI:dNDMI" = "FWI:\ndNDMI",
      "dNDMI:NDVI Prefire" = "dNDMI:\nNDVI Prefire",
      "dNDMI:Elevation" = "dNDMI:\nElevation")) +
 geom_text(data=ie_data3,aes(x=interaction,y=hstat, label=hstat, group=weather), size=1.5, position = position_dodge(width = 1)) +
  theme(legend.position =c(.90, .08),
              legend.title = element_text(size = 5),
              legend.text = element_text(size = 4),
        legend.key.size = unit(.05, "in"),
        legend.background = element_rect(fill=alpha('white', 0.0))) +
  guides(fill = guide_legend( ncol=1)) + 
  guides(shape = guide_legend(override.aes = list(size = 0.5))) + 
  guides(color = guide_legend(override.aes = list(size = 0.5)))
 
 
plot1
```



   #geom_label(data=ie_data3, aes(x=interaction, y=hstat, label = hstat, colour = weather), colour = "gray", nudge_x = 0.35, size = 3, position = position_dodge(width = 1))




```{r eval=FALSE, include=FALSE}
ggsave("../figures/TwoWayInteraction3FWI_v2.tiff", plot = plot1, width = 3, height =4, units = c("in"), dpi=600 )
```

```{r}
plot2 = ggplot(ie_data3) +
    geom_linerange(aes(x = interaction, ymin = 0, ymax = hstat, colour = weather), 
                   position = position_dodge(width = .25), show.legend = FALSE)+
    geom_point(aes(x = interaction, y = hstat, colour = weather),
               position = position_dodge(width = .25), size = 8) +
  
  geom_rect(data = shading, aes(xmin = min, xmax = max, ymin = -Inf, ymax = Inf, fill = factor(col), alpha = 0.1), show.legend = FALSE) +
  scale_fill_manual(values = c("white", "gray90")) +
  geom_linerange(aes(x = interaction, ymin = 0, ymax = hstat, colour = weather), 
                   position = position_dodge(width = .25), show.legend = FALSE)+
    geom_point(aes(x = interaction, y = hstat, colour = weather),
               position = position_dodge(width = .25), size = 8) +
  scale_colour_manual(values = c("#999999", "#D55E00", "#F0E442", "#56B4E9"), name = "Model", breaks = c("Full", "Extreme", "Moderate", "Benign"), labels=c("Full", "Extreme", "Moderate", "Benign"), guide = guide_legend(reverse=FALSE))  +
    coord_flip() +
    bar_theme +
  ylab('Two-way interaction strength') +
  scale_x_discrete(
    "Explanatory Variables",
    labels = c(
      "FWI:NDVI Prefire" = "FWI:\nNDVI Prefire",
      "FWI:Elevation" = "FWI:\nElevation",
      "Elevation:NDVI Prefire" = "Elevation:\nNDVI Prefire",
      "FWI:dNDMI" = "FWI:\ndNDMI",
      "dNDMI:NDVI Prefire" = "dNDMI:\nNDVI Prefire",
      "dNDMI:Elevation" = "dNDMI:\nElevation")) +
 geom_text(data=ie_data3,aes(x=interaction,y=hstat, label=hstat, group=weather), size=3, position = position_dodge(width = 1)) +
  theme(legend.position =c(.94, .08),
              legend.title = element_text(size = 6),
              legend.text = element_text(size = 5),
        legend.key.size = unit(.2, "in"),
        legend.background = element_rect(fill=alpha('white', 0))) +
  guides(fill = guide_legend( ncol=1)) + 
  guides(shape = guide_legend(override.aes = list(size = 0.5))) + 
  guides(color = guide_legend(override.aes = list(size = 0.5))) +
facet_wrap(~weather, nrow=2)

plot2
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/TwoWayInteraction3FWIWrap_v2.tiff", plot = plot2, width = 6, height =6, units = c("in"), dpi=600 )
```

```{r}
plot3 = ggplot(ie_data3) +
    geom_linerange(aes(x = interaction, ymin = 0, ymax = hstat, colour = weather), 
                   position = position_dodge(width = .25), show.legend = FALSE)+
    geom_point(aes(x = interaction, y = hstat, colour = weather),
               position = position_dodge(width = .25), size = 8) +
  
  geom_rect(data = shading, aes(xmin = min, xmax = max, ymin = -Inf, ymax = Inf, fill = factor(col), alpha = 0.1), show.legend = FALSE) +
  scale_fill_manual(values = c("white", "gray90")) +
  geom_linerange(aes(x = interaction, ymin = 0, ymax = hstat, colour = weather), 
                   position = position_dodge(width = .25), show.legend = FALSE)+
    geom_point(aes(x = interaction, y = hstat, colour = weather),
               position = position_dodge(width = .25), size = 8) +
  scale_colour_manual(values = c("#999999", "#D55E00", "#F0E442", "#56B4E9"), name = "Model", breaks = c("Full", "Extreme", "Moderate", "Benign"), labels=c("Full", "Extreme", "Moderate", "Benign"), guide = guide_legend(reverse=FALSE))  +
    coord_flip() +
    bar_theme +
  ylab('Two-way interaction strength') +
  scale_x_discrete(
    "Explanatory Variables",
    labels = c(
      "FWI:NDVI Prefire" = "FWI:\nNDVI Prefire",
      "FWI:Elevation" = "FWI:\nElevation",
      "Elevation:NDVI Prefire" = "Elevation:\nNDVI Prefire",
      "FWI:dNDMI" = "FWI:\ndNDMI",
      "dNDMI:NDVI Prefire" = "dNDMI:\nNDVI Prefire",
      "dNDMI:Elevation" = "dNDMI:\nElevation")) +
 geom_text(data=ie_data3,aes(x=interaction,y=hstat, label=hstat, group=weather), size=2.75, position = position_dodge(width = 1)) +
  theme(legend.position = "none") +
facet_wrap(~weather, nrow=2)

plot3
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/TwoWayInteraction3FWIWrap2_v2.tiff", plot = plot3, width = 6, height =6, units = c("in"), dpi=600 )
```