---
title: "LandTrendr Time Series"
author: "Anna Talucci"
date: "6/7/2021"
output: html_document
---

-

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview
LandTrendr Time Series Analysis
NBR, NDMI, and NDVI

# Packages
```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(RColorBrewer)
library(cowplot)
```

# Data
```{r}
chndmi = read.csv("../data/LT-TS/2019-04-04_chelaslie_pico_NDMI.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(chndmi)
```


```{r}
enndmi = read.csv("../data/LT-TS/2019-04-04_entiako_pico_NDMI.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(enndmi)
```

```{r}
twnmdi = read.csv("../data/LT-TS/2019-04-04_tweeds_pico_NDMI.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(twnmdi)
```

# Organize Data
## Chelaslie
### Extract Sourced Data
```{r}
chndmiorg2 = chndmi%>%dplyr::select(Year:Original)
chndmiorg2 = chndmiorg2%>%mutate(line_type = "raw")
chndmiorg2 = rename(chndmiorg2, year = Year, ndmi=Original, line_type=line_type)
chndmiorg2
```

### Extract Fitted Data
```{r}
chndmifit2 = chndmi%>%dplyr::select(Year, Fitted)
chndmifit2 = chndmifit2%>%mutate(line_type = "fit")
chndmifit2 = rename(chndmifit2, year = Year, ndmi=Fitted, line_type=line_type)
chndmifit2
```

### COmbine sourced and fitted data
```{r}
chndmi1 = rbind(chndmiorg2, chndmifit2)
summary(chndmi1)
```

## Entako

### Extract Sourced Data
```{r}
enndmiorg3 = enndmi %>% 
  dplyr::select(Year:Original) %>% 
  mutate(line_type = "raw") %>%
  rename(year = Year, ndmi=Original, line_type=line_type) %>%
  filter(ndmi > 0)
enndmiorg3
```

### Extract Fitted Data
```{r}
enndmifit3 = enndmi %>% 
  dplyr::select(Year, Fitted) %>%
  mutate(line_type = "fit") %>%
  rename(year = Year, ndmi=Fitted, line_type=line_type)

enndmifit3
```

### Combine sourced and Fitted Data
```{r}
enndmi1 = rbind(enndmiorg3, enndmifit3)
summary(enndmi1)
```

## Tweeds
### Extract Sourced Data
```{r}
twndmiorg4 = twnmdi%>%dplyr::select(Year:Original)
twndmiorg4=twndmiorg4%>%mutate(line_type = "raw")
twndmiorg4 = rename(twndmiorg4, year = Year, ndmi=Original, line_type=line_type)
twndmiorg4
```
### Extract Fitted Data
```{r}
twndmifit4 = twnmdi%>%dplyr::select(Year, Fitted)
twndmifit4 = twndmifit4%>%mutate(line_type = "fit")
twndmifit4 = rename(twndmifit4, year = Year, ndmi=Fitted, line_type=line_type)
twndmifit4
```
### Combine sourced and Fitted Data
```{r}
twnmdi1 = rbind(twndmiorg4, twndmifit4)
summary(twnmdi1)
```


# Graph Sourced and Fitted Data
## Chelaslie


```{r}
( chndmi1_plot1 = ggplot(chndmi1, aes(x = year, y = ndmi, color = line_type)) +
  geom_line(size=1) +
  scale_color_manual(values = c("#2b83ba", "#f03b20"), name="",
                         breaks=c("raw", "fit"),
                         labels=c("Source", "Fitted")) +
    ylab(label="NDMI") + 
  xlab("Year") +
  theme_bw() +
    geom_vline(aes(xintercept=2000), colour="darkorange2", linetype="dashed", size=1)  +
  geom_vline(aes(xintercept=2006), colour="darkorange2", linetype="dashed", size=1)  + 
  theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) )

```



## Entiako


```{r}

( enndmi1_plot1 = ggplot(enndmi1, aes(x = year, y = ndmi, color = line_type)) +
  geom_line(size=1) +
  scale_color_manual(values = c("#2b83ba", "#f03b20"), name="",
                         breaks=c("raw", "fit"),
                         labels=c("Source", "Fitted")) +
    ylab(label="NDMI") + 
  xlab("Year") +
  theme_bw() +
     geom_vline(aes(xintercept=2000), colour="darkorange2", linetype="dashed", size=1)  +
  geom_vline(aes(xintercept=2006), colour="darkorange2", linetype="dashed", size=1)  +  
  theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) )


```


## Tweeds 

```{r}
(twndmi1_plot1 = ggplot(twnmdi1, aes(x = year, y = ndmi, color = line_type)) +
  geom_line(size=1) +
  scale_color_manual(values = c("#2b83ba", "#f03b20"), name="",
                         breaks=c("raw", "fit"),
                         labels=c("Source", "Fitted")) +
    ylab(label="NDMI") + 
  xlab("Year") +
  geom_vline(aes(xintercept=2000), colour="darkorange2", linetype="dashed", size=1)  +
  geom_vline(aes(xintercept=2006), colour="darkorange2", linetype="dashed", size=1)  +
  theme_bw() +
       theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) )

```



# Figures
## Legend
```{r}
(legend_lt = ggplot(twnmdi1, aes(x = year, y = ndmi, color = line_type)) +
  geom_line(size=1) +
  scale_color_manual(values = c("#2b83ba", "#f03b20"), name="",
                         breaks=c("raw", "fit"),
                         labels=c("Source", "Fitted")) +
    ylab(label="NBR") + 
  xlab("Year") +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) )
```

## NDMI 
```{r fig.height=6, fig.width=3}
legend = cowplot::get_legend(legend_lt)

gpndmi7 = cowplot::plot_grid(enndmi1_plot1, twndmi1_plot1, chndmi1_plot1, align = "hv", ncol= 1)  +
  draw_label("Entiako", x = .29, y = .77, size = 10, fontface = "bold") +
  draw_label("Tweedsmuir", x = .33, y = .44, size = 10, fontface = "bold") +
  draw_label("Chelaslie", x = .30, y = .11, size = 10, fontface = "bold") +
  
   draw_label("(a)", x = .04, y = .98, size = 10) +
   draw_label("(b)", x = .04, y = .65, size = 10) +
   draw_label("(c)", x = .04, y = .32, size = 10)  

gpndmi7
```




```{r eval=FALSE, include=FALSE}
ggsave("../figures/LandTrendrTimeSeries.tiff", plot = gpndmi7, width = 3, height = 6, units = c("in"), dpi=600 )
```

**THE END**