---
title: "Map Figure"
author: "Anna Talucci"
date: '2022-08-26'
output: html_document
---

# Overview

Map figure for ERL BC paper

# Packages 
```{r}
library(terra)
library(gdalUtilities)
library(sf)
library(tidyverse)
library(tmap)
library(raster)
library(RColorBrewer)
```

# Data

## Polygons
```{r}
ch_forest = st_read("../data/perimeters-forest-only/ch_R10070_2014_Forestonly.shp", "ch_R10070_2014_Forestonly") 
en_forest = st_read("../data/perimeters-forest-only/en_R10171_2012_Forestonly.shp", "en_R10171_2012_Forestonly")
tw_forest = st_read("../data/perimeters-forest-only/tw_R10252_2013_Forestonly.shp", "tw_R10252_2013_Forestonly")
```

```{r}
en_poly = st_read("../data/perimeters/R10171.shp", "R10171") 
ch_poly = st_read("../data/perimeters/R10070.shp", "R10070")
tw_poly = st_read("../data/perimeters/R10252.shp", "R10252")
```

## Rasters

### FWI
```{r}
fwi_en<-rast("../data/fwi/2012-R10171_2012.rc1.tif")
fwi_ch<-rast("../data/fwi/R10070_2014.rc1.tif")
fwi_tw<-rast("../data/fwi/tw_fwi.tif")
```

```{r}
fwi_en
```

### dNBR

```{r}
rdnbr_en<-raster("../data/GEE_layers_forMaps/en_layers/en_rdnbr.tif")
rdnbr_ch<-raster("../data/GEE_layers_forMaps/ch_layers/ch_rdnbr.tif")
rdnbr_tw<-raster("../data/GEE_layers_forMaps/tw_layers/tw_rdnbr.tif")
```

### Beetles

```{r}
dndmi_en<-raster("../data/GEE_layers_forMaps/en_layers/withdndmi.tif")
dndmi_ch<-raster("../data/GEE_layers_forMaps/ch_layers/withdndmi.tif")
dndmi_tw<-raster("../data/GEE_layers_forMaps/tw_layers/withdndmi.tif")
```

```{r}
dndmi_tw
```
```{r}
dndmi_en
```

```{r}
plot(dndmi_tw)
```
### ndvi

```{r}
ndvi_en<-raster("../data/GEE_layers_forMaps/en_layers/ndviprefire.tif")
ndvi_ch<-raster("../data/GEE_layers_forMaps/ch_layers/ndviprefire.tif")
ndvi_tw<-raster("../data/GEE_layers_forMaps/tw_layers/ndviprefire.tif")
```

```{r}
ndvi_en
```
# VRI
# Fires Perimeters

## Data
```{r}
fires = st_read("../data/PROT_HISTORICAL_FIRE_POLYS_SP/H_FIRE_PLY_polygon.shp", "H_FIRE_PLY_polygon") 
```

## Select Fires
```{r}
en_fire = fires %>%
  filter(FIRE_YEAR>2011) %>%
  filter(FIRE_YEAR<2015) %>%
  filter(SIZE_HA>3000) %>%
  filter(FIRE_NO=="R10171" )

en_fire
```

```{r}
tw_fire = fires %>%
  filter(FIRE_YEAR>2011) %>%
  filter(FIRE_YEAR<2015) %>%
  filter(SIZE_HA>3000) %>%
  filter(FIRE_NO=="R10252")

tw_fire
```

```{r}
ch_fire = fires %>%
  filter(FIRE_YEAR>2011) %>%
  filter(FIRE_YEAR<2015) %>%
  filter(SIZE_HA>3000) %>%
  filter(FIRE_NO=="R10070" )

ch_fire
```
# VRI

## Data
```{r}
ch_vri= st_read("../data/VRI1/Chelaslie_VRI.shp", "Chelaslie_VRI") 
```

```{r}
en_vri= st_read("../data/VRI1/Entiako_VRI.shp", "Entiako_VRI") 
```

```{r}
tw_vri= st_read("../data/VRI1/Tweeds_VRI.shp", "Tweeds_VRI") 
```

```{r}
ch_vri_all= st_read("../data/VRI1/CH_2014_VRI.shp", "CH_2014_VRI") 
```

```{r}
en_vri_all= st_read("../data/VRI1/EN_2012_VRI.shp", "EN_2012_VRI") 
```

```{r}
tw_vri_all = st_read("../data/VRI1/TW_2013_VRI.shp", "TW_2013_VRI") 
```

# Select Data

```{r}
head(en_vri)
```

```{r}
unique(ch_vri$SPECIES_CD)
```

```{r}
unique(en_vri$BCLCS_LE_1)
```

# Select non veg
```{r}
en_water = en_vri_all %>% filter(BCLCS_LE_1=="W")
ch_water = ch_vri_all %>% filter(BCLCS_LE_1=="W")
tw_water = tw_vri_all %>% filter(BCLCS_LE_1=="W")
```

```{r}
plot(st_geometry(en_water))
```
```{r}
en_nonveg = en_vri_all %>% filter(BCLCS_LE_1=="N")
ch_nonveg = ch_vri_all %>% filter(BCLCS_LE_1=="N")
tw_nonveg = tw_vri_all %>% filter(BCLCS_LE_1=="N")
```

```{r}
plot(st_geometry(en_nonveg))
```
# Select Pine
```{r}
en_pine = en_vri %>% filter(SPECIES_CD=="PL")
ch_pine = ch_vri %>% filter(SPECIES_CD=="PL") 
tw_pine = tw_vri %>% filter(SPECIES_CD=="PL")
```

```{r}

percent_pine_en = sum(en_pine$SHAPE_Area)/sum(en_vri$SHAPE_Area)*100
percent_pine_en

percent_pine_ch = sum(ch_pine$SHAPE_Area)/sum(ch_vri$SHAPE_Area)*100
percent_pine_ch

percent_pine_tw = sum(tw_pine$SHAPE_Area)/sum(tw_vri$SHAPE_Area)*100
percent_pine_tw
```

```{r}
(sum(tw_pine$SHAPE_Area)+sum(ch_pine$SHAPE_Area)+sum(en_pine$SHAPE_Area))/(sum(tw_vri$SHAPE_Area)+sum(ch_vri$SHAPE_Area)+sum(en_vri$SHAPE_Area))*100
```

# Select not pine
# Select Pine
```{r}
en_nopine = en_vri %>% filter(SPECIES_CD!="PL")
ch_nopine = ch_vri %>% filter(BCLCS_LE_1!="W") %>% filter(!SPECIES_CD %in% c("PL", "PLI"))
tw_nopine = tw_vri %>% filter(SPECIES_CD!="PL")
```

```{r}
plot(st_geometry(ch_nopine))
```
# Projection

```{r}
zone10 = "+proj=utm +zone=10 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
zone9  = "+proj=utm +zone=9 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```

# Reproject Raster to UTM

```{r}
en_fwizone10 = project(fwi_en, zone10)
```

# Reporject polygons to UTM

```{r}
en_polyzone10 = st_transform(en_poly, crs = zone10)
ch_polyzone10 = st_transform(ch_poly, crs = zone10)
tw_polyzone9 = st_transform(tw_poly, crs = zone9)
```

```{r}
en_forestzone10 = st_transform(en_forest, crs = zone10)
ch_forestzone10 = st_transform(ch_forest, crs = zone10)
tw_forestzone9 = st_transform(tw_forest, crs = zone9)
tw_forestzone10 = st_transform(tw_forest, crs = zone10)
```

# Multipoly to poly

```{r}
en_zone10 <- st_cast(en_forestzone10$geometry, "POLYGON") %>% st_as_sf(.) %>% st_zm(.)
```

```{r}
ch_zone10 <- st_cast(ch_forestzone10$geometry, "POLYGON") %>% st_as_sf(.) %>% st_zm(.)
tw_zone9 <- st_cast(tw_forestzone9$geometry, "POLYGON") %>% st_as_sf(.) %>% st_zm(.)

tw_zone10 <- st_cast(tw_forestzone10$geometry, "POLYGON") %>% st_as_sf(.) %>% st_zm(.)
```


# Plots
```{r}
plot(ndvi_en)
plot(en_zone10, add=TRUE)
```
# Mask

## NDVI
```{r}
mask_ndvi_en = raster::mask(ndvi_en, en_zone10)
```

```{r}
mask_ndvi_ch = raster::mask(ndvi_ch, ch_zone10)
mask_ndvi_tw = raster::mask(ndvi_tw, tw_zone9)
```

## dNDMI

```{r}
mask_dndmi_en = raster::mask(dndmi_en,  en_zone10)
mask_dndmi_ch = raster::mask(dndmi_ch, ch_zone10)
mask_dndmi_tw = raster::mask(dndmi_tw, tw_zone10)
```

```{r}
mask_rdnbr_en = raster::mask(rdnbr_en,  en_zone10)
mask_rdnbr_ch = raster::mask(rdnbr_ch, ch_zone10)
mask_rdnbr_tw = raster::mask(rdnbr_tw, tw_zone9)
```


#tmap

## Polys
```{r}
map_en = tm_shape(en_poly) + tm_polygons(col="white")
```

```{r}
map_ch = tm_shape(ch_poly) + tm_polygons(col="white")
```

```{r}
map_tw = tm_shape(tw_poly) + tm_polygons(col="white")
```



## Bounding Box
```{r}
bbox_new <- st_bbox(tw_poly) # current bounding box

xrange <- bbox_new$xmax - bbox_new$xmin # range of x values
yrange <- bbox_new$ymax - bbox_new$ymin # range of y values

# bbox_new[1] <- bbox_new[1] - (0.5 * xrange) # xmin - left
bbox_new[3] <- bbox_new[3] + (0.5 * xrange) # xmax - right
# bbox_new[2] <- bbox_new[2] - (0.5 * yrange) # ymin - bottom
#  bbox_new[4] <- bbox_new[4] + (0.5 * yrange) # ymax - top

bbox_new <- bbox_new %>%  # take the bounding box ...
  st_as_sfc() # ... and make it a sf polygon
```

```{r}
st_bbox(en_poly)
```
## Breaks

```{r}
breaks_fwi = c(0, 13, 29, 50)
breaks_ndvi = c(0,  0.3, 0.5, 0.7, 1)
breaks_dndmi = c(-100, 0, 100, 200, 600)
breaks_rdnbr = c(0, 641, 1500)
```


## Labels for Legend
```{r}
labs_dndmi = c("Regrowth (<=-100", "Unchanged/low (>-100-100)", "Moderate mortality (>100-200)", "High mortality (>200)")
labs_ndvi = c("Dead/sparse (<=0.4)", "Mixed live/dead (>0.4-0.7)",  "Live/dense (>=0.8" )
labs_fwi = c("Benign (<=13)", "Moderate (>13-29)", "Extreme (>29)")
labs_rdnbr = c ("Other severity (<641)", "High Severity (>=641)")

lab_ndvi = c("0", "",  "0.5", "", "1" )
```
expression(phantom(x) >=80
## Palettes

```{r}

pal_dndmi = c('#018571','#80cdc1', '#dfc27d','#a6611a')
pal_ndvi = c("#7C7C7C", "#C3C3C3", "#F6FF97", "#96B566",  "#668E39")
pal_fwi = c('#4b7e75','#e5c850', '#d87641')
pal_rdnbr = c("#daf7a6", "#ffc300")
```

#Assemble Figure


## dNDMI

### aesthetics
labels=labs_dndmi

c(.63,0)


```{r}
beetle_legend = tm_raster(palette = pal_dndmi,  breaks = breaks_dndmi, title = "Outbreak Severity (dNDMI)", style = "cont",legend.is.portrait = FALSE) +              
  tm_layout(title = "(e)", 
                  title.size = .8, 
                  title.position = c(0, .90),
                  frame.lwd=2, frame = FALSE, 
                  legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.57, 0), 
            legend.width = 1, 
            legend.height = .22,
            legend.outside = FALSE )
```

```{r}
beetle_nolegend1 = tm_raster(palette = pal_dndmi, breaks = breaks_dndmi, legend.show = FALSE) + tm_layout( frame.lwd=2, frame = FALSE, title = "(d)", title.size = .8, title.position = c(0, .90))
```

```{r}
beetle_nolegend2 = tm_raster(palette = pal_dndmi, breaks = breaks_dndmi, legend.show = FALSE) + tm_layout( frame.lwd=2, frame = FALSE, title = "(f)", title.size = .8, title.position = c(0, .90))
```
### maps
```{r}
map_en1 = map_en + tm_shape(mask_dndmi_en) + beetle_nolegend1 

map_ch1 = map_ch + tm_shape(mask_dndmi_ch) + beetle_nolegend2

map_tw1 = map_tw + tm_shape(mask_dndmi_tw) + beetle_legend 
```

### gridded
```{r}
tmap_arrange(map_en1, map_tw1, map_ch1, nrow = 1, widths = .3, heights = .3)

```


## NDVI
legend.title.size = 1, legend.text.size = 0.6, legend.position = c(.68, 0), 
### aethestics
```{r}
ndvi_legend = tm_raster(palette = pal_ndvi, breaks=breaks_ndvi, labels = lab_ndvi, interval.closure = "left", title = "Prefire vegetation (NDVI)", style = "cont",legend.is.portrait = FALSE) + tm_layout(frame.lwd=2, frame = FALSE, 
                  legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.59, 0), 
            legend.width = 1, 
            legend.height = .22,
            legend.outside = FALSE,
             title = "(h)", title.size = .8, 
                  title.position = c(0, .90),)
```

```{r}
ndvi_nolegend3 = tm_raster(palette = pal_ndvi, breaks=breaks_ndvi, interval.closure = "left", legend.show = FALSE) + tm_layout(frame.lwd=2, frame = FALSE, title = "(g)", title.size = .8, 
                  title.position = c(0, .90),)
```

```{r}
ndvi_nolegend4 = tm_raster(palette = pal_ndvi, breaks=breaks_ndvi, interval.closure = "left", legend.show = FALSE) + tm_layout(frame.lwd=2, frame = FALSE, title = "(i)", title.size = .8, 
                  title.position = c(0, .90),)
```
### maps
```{r}
map_en2 = map_en + tm_shape(mask_ndvi_en) + ndvi_nolegend3

map_ch2 = map_ch + tm_shape(mask_ndvi_ch) + ndvi_nolegend4

map_tw2 = map_tw + tm_shape(mask_ndvi_tw) + ndvi_legend
```
### New Palette
```{r}
ndvi_pal2 = c('#a50026','#d73027','#f46d43','#fdae61','#fee08b','#ffffbf','#d9ef8b','#a6d96a','#66bd63','#1a9850','#006837')

ndvi_breaks2 = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0)

ndvi_labs2 = c("0", "", "", "", "", "0.5", "", "", "", "", "1")
```

,'#e0e0e0','#bababa','#878787','#4d4d4d','#1a1a1a'
```{r}
map_en_ndvi = map_en + tm_shape(mask_ndvi_en) +
  tm_raster(palette = ndvi_pal2, breaks=ndvi_breaks2, labels = ndvi_labs2, midpoint = 0.5, interval.closure = "left", title = "Prefire vegetation (NDVI)", style = "cont",legend.is.portrait = FALSE, legend.show = F) + 
  tm_layout(title = "(g)", 
            title.size = .8, 
            title.position = c(0, .90),
                  frame.lwd=2, 
                  frame = FALSE,
             legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.57, 0), 
            legend.width = 1, 
            legend.height = .25,
            legend.outside = FALSE)

map_en_ndvi
```

```{r}
map_tw_ndvi = map_tw + tm_shape(mask_ndvi_tw) +
  tm_raster(palette = ndvi_pal2, breaks=ndvi_breaks2, labels = ndvi_labs2, midpoint = 0.5, interval.closure = "left",title = "Prefire vegetation (NDVI)", style = "cont", legend.is.portrait = FALSE, legend.show = T) + 
  tm_layout(title = "(h)", 
            title.size = .8, 
            title.position = c(0, .90),
                  frame.lwd=2, 
                  frame = FALSE,
             legend.title.size = .75, 
                  legend.text.size = 0.6, 
                  legend.position = c(.52, 0), 
            legend.width = .5, 
            legend.height = .20,
            legend.outside = FALSE)

map_tw_ndvi
```

```{r}
map_ch_ndvi = map_ch + tm_shape(mask_ndvi_ch) +
  tm_raster(palette = ndvi_pal2, breaks=ndvi_breaks2, labels = ndvi_labs2, midpoint = 0.5, interval.closure = "left",title = "Prefire vegetation (NDVI)", style = "cont", legend.is.portrait = FALSE, legend.show = F) + 
  tm_layout(title = "(i)", 
            title.size = .8, 
            title.position = c(0, .90),
                  frame.lwd=2, 
                  frame = FALSE,
             legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.57, 0), 
            legend.width = 1, 
            legend.height = .25,
            legend.outside = FALSE)

map_ch_ndvi
```

### gridded
```{r height=1.5, fig.width=6}
tmap_arrange(map_en_ndvi, map_tw_ndvi, map_ch_ndvi, nrow = 1, widths = .3, heights = .3)
```

## FWI

### aestheitcs
```{r}
fwi_legend = tm_raster(palette = "YlOrRd", breaks = breaks_fwi, title = "Fire Weather (FWI)", style = "cont",legend.is.portrait = FALSE) + 
  tm_layout(frame.lwd=2, frame = FALSE, 
                 legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.59, 0), 
            legend.width = 1.5, 
            legend.height = .25,
            legend.outside = FALSE,  title = "(k)", title.size = .8, 
                  title.position = c(0, .90),)
```

```{r}
fwi_nolegend5 = tm_raster(palette = "YlOrRd",  breaks = breaks_fwi, legend.show = FALSE) + 
  tm_layout(frame.lwd=2, frame = FALSE, title = "(j)", title.size = .8, 
                  title.position = c(0, .90),)
```

```{r}
fwi_nolegend6 = tm_raster(palette = "YlOrRd",  breaks = breaks_fwi, legend.show = FALSE) + 
  tm_layout(frame.lwd=2, frame = FALSE, title = "(l)", title.size = .8, 
                  title.position = c(0, .90),)
```

### Maps
```{r}
map_en3 = map_en + tm_shape(fwi_en) + fwi_nolegend5

map_ch3 = map_ch + tm_shape(fwi_ch) + fwi_nolegend6

map_tw3 = map_tw + tm_shape(fwi_tw) + fwi_legend 
```

### gridded
```{r}
tmap_arrange(map_en3, map_tw3, map_ch3, nrow = 1, widths = .3, heights = .3)
```

## RdNBR
legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.5, 0), 
            legend.width = 1, 
            legend.height = .25,
### Aethetics
```{r}
rdnbr_legend = tm_raster(palette = pal_rdnbr, breaks = breaks_rdnbr, title = "Burn severity (RdNBR)", style = "cont",legend.is.portrait = FALSE) + 
  tm_layout(frame.lwd=2, frame = FALSE, 
            legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.63, .09), 
            legend.width = 1, 
            legend.height = .23,
            legend.outside = FALSE, title = "(n)", title.size = .8, 
                  title.position = c(0, .90)) + tm_scale_bar(breaks = c(0, 1, 2), width = .2, position = c(.33, 0), text.size=.4, lwd = .1)
```

```{r}
rdnbr_nolegend7 = tm_raster(palette = pal_rdnbr,  breaks = breaks_rdnbr, legend.show = FALSE) + 
  tm_layout(frame.lwd=2, frame = FALSE, title = "(m)", title.size = .8, 
                  title.position = c(0, .90)) +  tm_scale_bar(breaks = c(0, 2, 4), width = .15, position = c(.35, 0), text.size=.4, lwd = .1)
```

```{r}
rdnbr_nolegend8 = tm_raster(palette = pal_rdnbr,  breaks = breaks_rdnbr, legend.show = FALSE) + 
  tm_layout(frame.lwd=2, frame = FALSE, title = "(o)", title.size = .8, 
                  title.position = c(0, .90)) +  tm_scale_bar(breaks = c(0, 10, 20), width = .2, position = c(.45, 0), text.size=.4, lwd = .1)
```

### Maps
```{r}
map_en4 = map_en + tm_shape(mask_rdnbr_en,) + rdnbr_nolegend7

map_ch4 = map_ch + tm_shape(mask_rdnbr_ch) + rdnbr_nolegend8

map_tw4 = map_tw + tm_shape(mask_rdnbr_tw)  +  rdnbr_legend
```

### gridded
```{r fig.height=1.5, fig.width=6}
tmap_arrange(map_en4, map_tw4, map_ch4, nrow = 1, widths = .3, heights = .3)

```

# All
```{r fig.height=7, fig.width=6}
map_grid = tmap_arrange( map_en1, map_tw1, map_ch1, map_en2, map_tw2, map_ch2, map_en3, map_tw3, map_ch3, map_en4, map_tw4, map_ch4, nrow = 4, widths = .3, heights = .3)

map_grid

```

```{r eval=FALSE, include=FALSE}
tmap_save(map_grid, "../figures/MappedVariables.png",  width = 6, height = 6, units = c("in"), dpi=600 )


```

# VRI With tmap
# Palettes
```{r}
pal_ch_nopine = c("#B35806", "#E08214", "#FDB863", "#F7F7F7", "#D8DAEB", "#B2ABD2", "#8073AC", "#542788")
pal_en_nopine = c("#E08214", "#F7F7F7", "#D8DAEB", "#8073AC")
pal_tw_nopine = c("#B35806", "#E08214", "#FDB863", "#FEE0B6", "#8073AC","#542788")
```
"#B35806" "#E08214" "#FDB863" "#FEE0B6" "#D8DAEB" "#B2ABD2" "#8073AC" "#542788"
 "PL"        "PLI"      

```{r}
breaks_nopine = c("AC",  "AT",  "BL", "L", "S", "SB", "SE", "SW",  "SX", "Missing" )
pal_nopine = c("#B35806", "#E08214", "#FDB863", "#FEE0B6", "#F7F7F7", "#D8DAEB", "#B2ABD2", "#8073AC", "#542788", "#C0C0C0")
```

## Bounding Box
```{r}
st_bbox(en_fire)
```

```{r}
bbox_en = st_bbox( c(xmin =1020745.6, ymin =901900.2, xmax = 1038355.2, ymax= 916902.9 ))
bbox_tw = st_bbox( c(xmin =985229.8, ymin =916146.9, xmax = 997233.6, ymax= 925038.5))
bbox_ch = st_bbox( c(xmin =998102.4, ymin =892874.2, xmax = 1069842.7, ymax= 940427.2))
```
     xmin      ymin      xmax      ymax 
1023087.6  903570.8 1037586.7  914616.2 

```{r}
st_bbox(en_pine)
st_bbox(tw_pine)
st_bbox(ch_pine)
```

## Fires for VRI
### Define Breaks
```{r}
my_breaks <- c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
my_breaks1 <- c(40, 50, 60, 70, 80, 90, 100)
my_breaks2 <- c(25, 50, 75, 100)
```

### Max for legend
```{r}
max_size <- max(c(tw_nopine$SPECIES_CD, ch_nopine$SPECIES_CD))
```


### EN

```{r}
map_en_vri = tm_shape(en_fire, bbox =bbox_en) + tm_polygons(col="#C0C0C0") +
  tm_shape(en_water, bbox =bbox_en) + tm_fill(col = "#5d89ba", border.col= "#5d89ba", title = "Water", legend.show = TRUE) + 
  tm_shape(en_nopine, bbox =bbox_en) + tm_fill(col = "SPECIES_CD", palette = pal_en_nopine, breaks = breaks_nopine, style="fixed", legend.show = FALSE) +
  tm_shape(en_pine, bbox =bbox_en) + tm_fill(col = "SPECIES_PC", palette = "YlGn", breaks = my_breaks2, style = "cont",title = "Percent pine", legend.show = FALSE) +
  tm_layout( main.title = "Entiako fire (2012)", 
             main.title.size = .9, 
             main.title.position=c("center", "top"),
             title = "(a)", title.size = .8, title.position = c(0, .90),
                  frame.lwd=2, 
                  frame = FALSE,
             legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.57, 0), 
            legend.width = 1, 
            legend.height = .25,
            legend.outside = FALSE)
```


```{r}
map_en_vri
```


### CH
```{r}
breaks_nopine = c("AC",  "AT",  "BL", "L", "S", "SB", "SE", "SW",  "SX", "Missing" )
pal_nopine = c("#B35806", "#E08214", "#FDB863", "#FEE0B6", "#F7F7F7", "#D8DAEB", "#B2ABD2", "#8073AC", "#542788", "#C0C0C0")
```

```{r}
map_ch_vri = tm_shape(ch_fire, bbox =bbox_ch) + tm_polygons(col="#C0C0C0") +
  tm_shape(ch_water, bbox =bbox_ch) + tm_polygons(col = "#5d89ba", border.col= "#5d89ba") + 
  tm_shape(ch_nopine, bbox =bbox_ch) + tm_fill(col = "SPECIES_CD", palette = pal_ch_nopine, title = "Other Species",legend.show = FALSE) +
  tm_shape(ch_pine, bbox =bbox_ch) +tm_fill(col = "SPECIES_PC", palette = "YlGn", breaks = my_breaks2, style = "cont",title = "Percent pine", legend.show = FALSE) +
  tm_layout( main.title = "Chelaslie fire (2014)", 
             main.title.size = .9, 
             main.title.position=c("center", "top"), 
             title = "(c)", 
                  title.size = .8, 
                  title.position = c(0, .90),
                  frame.lwd=2, 
             frame = FALSE,
             legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.75, 0), 
            legend.width = 1, 
            legend.height = .6,
            legend.outside = FALSE ) +
  tm_add_legend(type = 'fill', 
                 col = pal_nopine,
                 border.col = NA,
                 labels = breaks_nopine,
                 title="Other Species")
```

```{r}
map_ch_vri
```

### TW
```{r}
map_tw_vri = tm_shape(tw_fire, bbox =bbox_tw) + tm_polygons(col="#C0C0C0") +
  tm_shape(tw_water, bbox =bbox_tw) + tm_polygons(col = "#5d89ba", border.col= "#5d89ba") + 
  tm_shape(tw_nopine, bbox =bbox_tw) + tm_fill(col = "SPECIES_CD", palette = pal_tw_nopine, title = "Other Species",legend.show = FALSE) +
  tm_shape(tw_pine, bbox =bbox_tw) +tm_fill(col = "SPECIES_PC", palette = "YlGn", breaks = my_breaks2, style = "cont",title = "Percent pine", legend.is.portrait = FALSE)  +
  tm_layout(main.title = "Tweedsmuir fire (2013)", 
                  main.title.size = .9, 
                  main.title.position=c("center", "top"), 
            title = "(b)", 
                  title.size = .8, 
                  title.position = c(0, .90),
                  frame.lwd=2, frame = FALSE, 
                  legend.title.size = .8, 
                  legend.text.size = 0.6, 
                  legend.position = c(.7, 0), 
            legend.width = 1, 
            legend.height = .3,
            legend.outside = FALSE )
```

```{r}
map_tw_vri
```

### gridded
```{r}
tmap_arrange(map_en_vri, map_tw_vri, map_ch_vri, nrow = 1, widths = .3, heights = .3)

```

# All with VRI
```{r fig.height=7, fig.width=6}
map_grid2 = tmap_arrange( map_en_vri, map_tw_vri, map_ch_vri, map_en1, map_tw1, map_ch1, map_en_ndvi, map_tw_ndvi, map_ch_ndvi, map_en3, map_tw3, map_ch3, map_en4, map_tw4, map_ch4, nrow = 5, widths = .3, heights = .3)

map_grid2

```

```{r eval=FALSE, include=FALSE}
tmap_save(map_grid2, "../figures/MappedVariablesPlusVRI.png",  width = 6, height = 7, units = c("in"), dpi=600 )
```
**THE END**