---
title: "150 Sample"
author: "Anna Talucci"
date: '2022-09-15'
output: html_document
---

```{r}
library(tidyverse)
library(sf)
library(RColorBrewer)
library(cowplot)
library(ggpmisc)
```
# Projections
WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "
```


# Data

## MPB Data
```{r}
mpb1999= st_read("../data/mpb_poly_1997to2011/ibm_poly_1999.shp", "ibm_poly_1999") 
```
```{r}
mpb2000= st_read("../data/mpb_poly_1997to2011/ibm_poly_2000.shp", "ibm_poly_2000") 
```
```{r}
mpb2001= st_read("../data/mpb_poly_1997to2011/ibm_poly_2001.shp", "ibm_poly_2001") 
```

```{r}
mpb2002= st_read("../data/mpb_poly_1997to2011/ibm_poly_2002.shp", "ibm_poly_2002") 
```

```{r}
mpb2003= st_read("../data/mpb_poly_1997to2011/ibm_poly_2003.shp", "ibm_poly_2003") 
```

```{r}
mpb2004= st_read("../data/mpb_poly_1997to2011/ibm_poly_2004.shp", "ibm_poly_2004") 
```

```{r}
mpb2005= st_read("../data/mpb_poly_1997to2011/ibm_poly_2005.shp", "ibm_poly_2005") 
```

```{r}
mpb2006= st_read("../data/mpb_poly_1997to2011/ibm_poly_2006.shp", "ibm_poly_2006") 
```

```{r}
mpb2007= st_read("../data/mpb_poly_1997to2011/ibm_poly_2007.shp", "ibm_poly_2007") 
```

## VRI 
```{r}
en_vri= st_read("../data/VRI1/Entiako_VRI.shp", "Entiako_VRI") 
```

```{r}
tw_vri= st_read("../data/VRI1/Tweeds_VRI.shp", "Tweeds_VRI") 
```

```{r}
ch_vri_all= st_read("../data/VRI1/CH_2014_VRI.shp", "CH_2014_VRI") 
```

## Perimeters

## Data
```{r}
fires = st_read("../data/PROT_HISTORICAL_FIRE_POLYS_SP/H_FIRE_PLY_polygon.shp", "H_FIRE_PLY_polygon") 
```

## Select Fires
```{r}
fire3 = fires %>%
  filter(FIRE_YEAR>2011) %>%
  filter(FIRE_YEAR<2015) %>%
  filter(SIZE_HA>3000) %>%
  filter(FIRE_NO %in% c("R10171", "R10252", "R10070"))

fire3
```



## Sampled points
```{r}
ch_df = read.csv("../data/2.1-GEE-Sampled/2021-06-07_ChSampledValues.csv", header=TRUE, sep = ",", strip.white = TRUE)
en_df = read.csv("../data/2.1-GEE-Sampled/2021-06-07_EnSampledValues.csv", header=TRUE, sep = ",", strip.white = TRUE)
tw_df = read.csv("../data/2.1-GEE-Sampled/2021-06-07_TwSampledValues.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

### Full data
```{r}
df = read.csv("../data/CombinedData/CombineDataCat3FWI.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

# Look at data
```{r}
head(df)
head(ch_df)
```
```{r}
unique(df$FireYr)
```

```{r}
df %>% filter(FireYr==2014)
```

# Subset 150
```{r}
set.seed(10)
df_subset = df %>% 
  dplyr::select(LAT, LON, dnbr, dndmi, ndviprefire, FireYr) %>% 
   group_by(FireYr) %>%
  filter_at(vars(LAT,LON),any_vars(!is.na(.))) %>%
  sample_n(., 150, replace = FALSE)
```

```{r}

```

```{r}
unique(df_subset$FireYr)
```
# Subset individual data samples
```{r}
set.seed(10)
ch_df_subset = ch_df %>% 
  dplyr::select(LAT, LON, dnbr, dndmi, ndviprefire) %>% 
  filter_at(vars(LAT,LON),any_vars(!is.na(.))) %>%
  sample_n(., 100, replace = FALSE) %>%
  mutate(FireYr=2014)
```

```{r}
set.seed(10)
tw_df_subset = tw_df %>% 
  dplyr::select(LAT, LON, dnbr, dndmi, ndviprefire) %>% 
  filter_at(vars(LAT,LON),any_vars(!is.na(.))) %>%
  sample_n(., 40, replace = FALSE) %>%
  mutate(FireYr=2013)
```

```{r}
set.seed(10)
en_df_subset = en_df %>% 
  dplyr::select(LAT, LON, dnbr, dndmi, ndviprefire) %>% 
  filter_at(vars(LAT,LON),any_vars(!is.na(.))) %>%
  sample_n(., 60, replace = FALSE) %>%
  mutate(FireYr=2012)
```


# Convert to points

```{r}
df_subset_pt = st_as_sf(df_subset, coords = c("LON", "LAT"), crs = wgs_proj)
```


```{r}
ch_subset_pt = st_as_sf(ch_df_subset, coords = c("LON", "LAT"), crs = wgs_proj)
en_subset_pt = st_as_sf(en_df_subset, coords = c("LON", "LAT"), crs = wgs_proj)
tw_subset_pt = st_as_sf(tw_df_subset, coords = c("LON", "LAT"), crs = wgs_proj)
```


```{r}
plot(st_geometry(df_subset_pt))
```

# Transform to VRI projection

```{r}
vri_project = st_crs(tw_vri)
```

```{r}
df_subset_pt_vri = st_transform(df_subset_pt, crs = vri_project)
```

```{r}
ch_pt_vri = st_transform(ch_subset_pt, crs = vri_project)
en_pt_vri = st_transform(en_subset_pt, crs = vri_project)
tw_pt_vri = st_transform(tw_subset_pt, crs = vri_project)
```

# Filter by fire year

```{r}
tw_pt = df_subset_pt_vri %>% filter(FireYr ==2013)
en_pt = df_subset_pt_vri %>% filter(FireYr ==2012)
```

# Overlay

```{r}
tw_data = st_join(tw_pt_vri, tw_vri)
en_data = st_join(en_pt_vri, en_vri)
ch_data = st_join(ch_pt_vri, ch_vri)
```

```{r}
tw_data
```

# Combine data frames
```{r}
combo_data = rbind(tw_data, en_data)
combo_data1 = rbind(combo_data, ch_data)
```

```{r}
combo_data1
```
```{r}
combo_data2 = combo_data1 %>% filter_at(vars(SPECIES_CD),all_vars(!is.na(.)))
```

# Add MPB data
```{r}
combo3 = combo_data2 %>% dplyr::select(dnbr, dndmi, ndviprefire, FireYr, SPECIES_CD, SPECIES_PC, BASAL_AREA, LIVE_VOL_P, DEAD_VOL_P)
combo3
```
```{r}
combo_mpb2000 = st_join(combo3, mpb2000)
combo_mpb2000
```

```{r}
combo_mpb2001 = st_join(combo3, mpb2001)
combo_mpb2002 = st_join(combo3, mpb2002)
combo_mpb2003 = st_join(combo3, mpb2003)
combo_mpb2004 = st_join(combo3, mpb2004)
combo_mpb2005 = st_join(combo3, mpb2005)
combo_mpb2006 = st_join(combo3, mpb2006)
combo_mpb2007 = st_join(combo3, mpb2007)

```

```{r}
unique(combo_mpb2003$SEVERITY)
```
# VRI species Palette

```{r}
brewer.pal(12, "PuOr")

# [1] "#A6CEE3" "#1F78B4" "#B2DF8A" "#33A02C" "#FB9A99" "#E31A1C"
# [7] "#FDBF6F" "#FF7F00" "#CAB2D6" "#6A3D9A" "#FFFF99" "#B15928"

# to display that palette:
display.brewer.pal(12, "PuOr")
```
"#F7F7F7", "#D8DAEB", "#8073AC", "#542788"

S = "#D8DAEB"
SB = "#B2ABD2", 
SE = "#8073AC", 
SW = "#542788", 
SX = "#2D004B",
```{r}
breaks_nopine = c("AC",  "AT",  "BL", "L", "S", "SB", "SE", "SW",  "SX", "Missing" )
pal_nopine = c("#B35806", "#E08214", "#FDB863", "#FEE0B6", "#D8DAEB", "#B2ABD2", "#8073AC", "#542788", "#2D004B", "#C0C0C0")
```

```{r}
brewer.pal(8, "YlGn")

# [1] "#A6CEE3" "#1F78B4" "#B2DF8A" "#33A02C" "#FB9A99" "#E31A1C"
# [7] "#FDBF6F" "#FF7F00" "#CAB2D6" "#6A3D9A" "#FFFF99" "#B15928"

# to display that palette:
display.brewer.pal(8, "YlGn")
```
# Plots

## NDVI Basal Area
```{r}
summary(lm(ndviprefire ~ BASAL_AREA, combo_data2))
```
```{r}
lm_eqn1 <- function(df){
    m <- lm(ndviprefire ~ BASAL_AREA, combo_data2);
    eq <- substitute(~~italic(r)^2~"="~r2, 
         list(r2 = format(summary(m)$r.squared, digits = 2)))
    as.character(as.expression(eq));
}
```

```{r}
ndvi_basal = ggplot(data = combo_data2, aes(x= BASAL_AREA, y = ndviprefire, color = SPECIES_CD)) +
  geom_point() +
  scale_color_manual(values = c("#E08214",  "#005A32",  "#D8DAEB", "#8073AC", "#B2ABD2",  "#542788"), name="Dominant species",
                         breaks=c("AT", "PL", "S", "SB", "SW",  "SX")) +
  labs(x="Basal area (square meters per hectare)", y="NDVI") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
 geom_text(x = 45, y = 0.5, label = lm_eqn1(df), parse = TRUE, colour="black", size=2)

ndvi_basal
```

## Whole stem
```{r}
summary(lm(ndviprefire ~ WHOLE_STEM, combo_data2))
```
```{r}
lm_eqn2 <- function(df){
    m <- lm(ndviprefire ~ WHOLE_STEM, combo_data2);
    eq <- substitute(~~italic(r)^2~"="~r2, 
         list(r2 = format(summary(m)$r.squared, digits = 2)))
    as.character(as.expression(eq));
}
```
```{r}
ndvi_wholestem = ggplot(data = combo_data2, aes(x= WHOLE_STEM, y = ndviprefire, color = SPECIES_CD)) +
  geom_point() +
  scale_color_manual(values = c("#E08214",  "#005A32",  "#D8DAEB", "#8073AC", "#B2ABD2",  "#542788"), name="Dominant species",
                         breaks=c("AT", "PL", "S", "SB", "SW",  "SX")) +
  labs(x="Whole stem biomass per hectare", y="NDVI") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
 geom_text(x = 175, y = 0.5, label = lm_eqn2(df), parse = TRUE, colour="black", size=2)

ndvi_wholestem
```
```{r}
breaks_nopine = c("AC",  "AT",  "BL", "L", "S", "SB", "SE", "SW",  "SX", "Missing" )
pal_nopine = c("#B35806", "#E08214", "#FDB863", "#FEE0B6", "#F7F7F7", "#D8DAEB", "#B2ABD2", "#8073AC", "#542788", "#C0C0C0")
```

```{r}
brewer.pal(8, "YlGn")

# [1] "#A6CEE3" "#1F78B4" "#B2DF8A" "#33A02C" "#FB9A99" "#E31A1C"
# [7] "#FDBF6F" "#FF7F00" "#CAB2D6" "#6A3D9A" "#FFFF99" "#B15928"

# to display that palette:
display.brewer.pal(8, "YlGn")
```

## Dead v MPB
```{r}
summary(lm(dndmi ~ DEAD_VOL_P, combo_data2))
```
```{r}
lm_eqn3 <- function(df){
    m <- lm(dndmi ~ DEAD_VOL_P, combo_data2);
    eq <- substitute(~~italic(r)^2~"="~r2, 
         list(r2 = format(summary(m)$r.squared, digits = 2)))
    as.character(as.expression(eq));
}
```

```{r}
dndmi_dead = ggplot(data = combo_data2, aes(x= DEAD_VOL_P, y = dndmi, color = SPECIES_CD)) +
  geom_point() +
  scale_color_manual(values = c("#E08214",  "#005A32",  "#D8DAEB", "#8073AC", "#B2ABD2",  "#542788"), name="Dominant species",
                         breaks=c("AT", "PL", "S", "SB", "SW",  "SX")) +
  labs(x="Dead volume per hectare", y="dNDMI") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
 geom_text(x = 325, y =-150, label = lm_eqn3(df), parse = TRUE, colour="black", size=2)

dndmi_dead
```
## Live v ndvi
```{r}
summary(lm(ndviprefire ~ LIVE_VOL_P, combo_data2))
```
```{r}
lm_eqn4 <- function(df){
    m <- lm(ndviprefire ~ LIVE_VOL_P, combo_data2);
    eq <- substitute(~~italic(r)^2~"="~r2, 
         list(r2 = format(summary(m)$r.squared, digits = 2)))
    as.character(as.expression(eq));
}
```

```{r}
ndvi_live = ggplot(data = combo_data2, aes(x= LIVE_VOL_P, y = ndviprefire, color = SPECIES_CD)) +
  geom_point() +
  scale_color_manual(values = c("#E08214",  "#005A32",  "#D8DAEB", "#8073AC", "#B2ABD2",  "#542788"), name="Dominant species",
                         breaks=c("AT", "PL", "S", "SB", "SW",  "SX")) +
  labs(x="Live volume per hectare", y="NDVI") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
 geom_text(x = 180, y =0.52, label = lm_eqn4(df), parse = TRUE, colour="black", size=2)
 
ndvi_live
```

## Crown closure v ndvi
```{r}
summary(lm(ndviprefire ~ CROWN_CLOS, combo_data2))
```
```{r}
lm_eqn5 <- function(df){
    m <- lm(ndviprefire ~ CROWN_CLOS, combo_data2);
    eq <- substitute(~~italic(r)^2~"="~r2, 
         list(r2 = format(summary(m)$r.squared, digits = 2)))
    as.character(as.expression(eq));
}
```

```{r}
ndvi_crown = ggplot(data = combo_data2, aes(x= CROWN_CLOS, y = ndviprefire, color = SPECIES_CD)) +
  geom_point() +
  scale_color_manual(values = c("#E08214",  "#005A32",  "#D8DAEB", "#8073AC", "#B2ABD2",  "#542788"), name="Dominant species",
                         breaks=c("AT", "PL", "S", "SB", "SW",  "SX")) +
  labs(x="Crown closure (%)", y="NDVI") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
 geom_text(x = 80, y =0.52, label = lm_eqn5(df), parse = TRUE, colour="black", size=2)

ndvi_crown
```
## Percent species v ndvi
```{r}
summary(lm(ndviprefire ~ SPECIES_PC, combo_data2))
```

```{r}
lm_eqn6 <- function(df){
    m <- lm(ndviprefire ~ SPECIES_PC, combo_data2);
    eq <- substitute(~~italic(r)^2~"="~r2, 
         list(r2 = format(summary(m)$r.squared, digits = 2)))
    as.character(as.expression(eq));
}
```


```{r}
ndvi_percent = ggplot(data = combo_data2, aes(x= SPECIES_PC, y = ndviprefire, color = SPECIES_CD)) +
  geom_point() +
  scale_color_manual(values = c("#E08214",  "#005A32",  "#D8DAEB", "#8073AC", "#B2ABD2",  "#542788"), name="Dominant species",
                         breaks=c("AT", "PL", "S", "SB", "SW",  "SX")) +
  labs(x="Species percent", y="NDVI") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
 geom_text(x = 52, y =0.51, label = lm_eqn6(df), parse = TRUE, colour="black", size=2)

ndvi_percent
```

```{r}
bottom_legend = ggplot(data = combo_data2, aes(x= SPECIES_PC, y = ndviprefire, color = SPECIES_CD)) +
  geom_point() +
  scale_color_manual(values = c("#E08214",  "#005A32",  "#D8DAEB", "#8073AC", "#B2ABD2",  "#542788"), name="Dominant species",
                         breaks=c("AT", "PL", "S", "SB", "SW",  "SX")) +
  labs(x="Species percent", y="NDVI") +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.title = element_text(size = 8),
              legend.text = element_text(size = 7) ) +
  guides(color=guide_legend(nrow=1))

bottom_legend 
```

# Gridded plots VRI
```{r}
legend = cowplot::get_legend(bottom_legend)
```

```{r fig.height=6, fig.width=6}

grid_plot1 = cowplot::plot_grid( ndvi_basal, ndvi_wholestem, ndvi_percent, ndvi_crown, ndvi_live, dndmi_dead, align = "hv", ncol= 2)  

grid_plot1
```

```{r fig.height=6, fig.width=6}
plot_vri1 = plot_grid(grid_plot1, legend, ncol=1, rel_widths = c(1, .1), rel_heights = c(1, .05)) +
   draw_label("(a)", x = .02, y = .985, size = 10) +
   draw_label("(b)", x = .52, y = .985, size = 10) +
   draw_label("(c)", x = .02, y = .675, size = 10) +
   draw_label("(d)", x = .52, y = .675, size = 10) +
   draw_label("(e)", x = .02, y = .36, size = 10) +
   draw_label("(f)", x = .52, y = .36, size = 10) 

plot_vri1
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/150SampleVRI.jpeg", plot = plot_vri1, width = 6, height = 6, units = c("in"), dpi=600, bg = "white")
```


# Plot MPB
```{r}
brewer.pal(12, "Spectral")

# [1] "#A6CEE3" "#1F78B4" "#B2DF8A" "#33A02C" "#FB9A99" "#E31A1C"
# [7] "#FDBF6F" "#FF7F00" "#CAB2D6" "#6A3D9A" "#FFFF99" "#B15928"

# to display that palette:
display.brewer.pal(12, "Spectral")
```

```{r}
mpb_breaks = c("T","L", "M", "S", "V", "X", NA)
mpb_palette = c("#2B83BA", "#ABDDA4", "#FFFFBF", "#FDAE61", "#D7191C", "#5E4FA2", "#542788")
```

```{r}
SEVERITY = c("T","L", "M", "S", "V", "X", NA)
SPECIES = c("AT", "PL", "S", "SB", "SW",  "SX")
numbers1 = c(1, 2, 3, 4, 5, 6, 7)
numbers3 = c(7, 6, 5, 4, 3, 2, 1)
numbers2 = c(1, 2, 3, 4, 5, 6)
numbers4 = c(6, 5, 4, 3, 2, 1)
df_Severity_legend = data.frame(SEVERITY, numbers1, numbers3)
df_species_legend = data.frame(SPECIES, numbers2, numbers4)
```

```{r}
legend_mpb = ggplot() +
  geom_point(data = df_Severity_legend, aes(x= numbers1, y = numbers3, color=SEVERITY)) +
  geom_point(data=df_species_legend, aes(x= numbers2, y = numbers4, shape = SPECIES)) +
  scale_color_manual(values = mpb_palette, name="Outbreak severity",
                         breaks=mpb_breaks) +
  scale_shape(name="Dominant species") +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1),
        legend.title = element_text(size = 8),
              legend.text = element_text(size = 7), 
        legend.justification = 'center', 
        legend.position = 'bottom', legend.box = 'vertical', 
        legend.box.just = 'left', 
        legend.margin = margin(-15, 0, 0, 0)) +
  guides(color=guide_legend(nrow=1), shape=guide_legend(nrow=1))

legend_mpb
```

```{r}
plot_mpb2000 = ggplot(data = combo_mpb2000, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="2000 Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2000") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2000
```
```{r}
plot_mpb2001 = ggplot(data = combo_mpb2001, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="2001 Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2001") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2001
```

```{r}
plot_mpb2002 = ggplot(data = combo_mpb2002, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="2002 Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2002") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2002
```
```{r}
plot_mpb2003 = ggplot(data = combo_mpb2003, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="2003 Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2003") +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2003
```

```{r}
plot_mpb2004 = ggplot(data = combo_mpb2004, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="2004 Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2004") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2004
```

```{r}
plot_mpb2005 = ggplot(data = combo_mpb2005, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="2005 Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2005") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2005
```

```{r}
plot_mpb2006 = ggplot(data = combo_mpb2006, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="2006 Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2006") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2006
```

```{r}
plot_mpb2007 = ggplot(data = combo_mpb2007, aes(x= BASAL_AREA, y = ndviprefire)) +
  geom_point(aes(color=SEVERITY, shape=SPECIES_CD)) +
  scale_color_manual(values = mpb_palette, name="Outbreak Severity",
                         breaks=mpb_breaks) +
  labs(x="Basal Area", y="NDVI", subtitle = "2007") +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size =9, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.subtitle = element_text(hjust = 0.1, size = 9)) +
  guides(color=guide_legend(nrow=1))

plot_mpb2007
```

# Gridded plots
```{r}
legend = cowplot::get_legend(legend_mpb)
```

```{r fig.height=6, fig.width=6}

grid_mpb1 = cowplot::plot_grid(plot_mpb2000, plot_mpb2001, plot_mpb2002, plot_mpb2003, plot_mpb2004, plot_mpb2005, plot_mpb2006, plot_mpb2007, align = "hv", ncol= 2)  

grid_mpb1
```

```{r fig.height=7, fig.width=6}
plot_mpb2 = plot_grid(grid_mpb1, legend, ncol=1, rel_widths = c(1, .1), rel_heights = c(1, .08)) 

plot_mpb2
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/150SampleMPB.jpeg", plot = plot_mpb2, width = 6, height = 7, units = c("in"), dpi=600, bg = "white")
```